### 2022-03-07 paper/localpsf.tex
commit changes before meeting

We use approximation \eqref{eq:translate3}, which is an improvement upon \eqref{eq:translate1} and \eqref{eq:translate2} that generalizes both. On one hand, if \eqref{eq:translate1} holds, then $\mu(x) \approx \mu(x_i)$, and so \eqref{eq:translate3} holds. On the other hand, translating a distribution translates its mean, so if \eqref{eq:translate2} holds, then $\mu(x_i)-\mu(x) \approx x_i - x$, so again \eqref{eq:translate3} holds. Furthermore, approximation \eqref{eq:translate3} can hold in situations where neither \eqref{eq:translate1} nor \eqref{eq:translate2} holds. For example, \eqref{eq:translate3} will hold when an operator is locally translation-invariant with respect to a rotated frame of reference, while \eqref{eq:translate2} will not hold in this case. Additionally, \eqref{eq:translate3} generalizes to operators $\Aop:L^2(\Omega_1) \rightarrow L^2(\Omega_2)'$ that map between function spaces on different domains $\Omega_1$ and $\Omega_2$, and even operators that map between domains with different spatial dimensions. In contrast, \eqref{eq:translate2} does not naturally generalize to operators that map between function spaces on different domains, because the formula $y-x+x'$ requires $y \in \Omega_2$ and $-x+x' \in \Omega_1$ to be added together.

>>>>

We use approximation \eqref{eq:translate3}, which is an improvement upon \eqref{eq:translate1} and \eqref{eq:translate2} that generalizes both. On one hand, if \eqref{eq:translate1} holds, then $\mu(x) \approx \mu(x_i)$, and so \eqref{eq:translate3} holds. On the other hand, translating a distribution translates its mean, so if \eqref{eq:translate2} holds, then $\mu(x_i)-\mu(x) \approx x_i - x$, so again \eqref{eq:translate3} holds. Furthermore, approximation \eqref{eq:translate3} can hold in situations where neither \eqref{eq:translate1} nor \eqref{eq:translate2} holds. For example, because the expected value is a linear operator, \eqref{eq:translate3} will hold when an $\Aop$ is locally translation-invariant with respect to a rotated frame of reference, while \eqref{eq:translate2} will not hold in this case. Additionally, \eqref{eq:translate3} generalizes to operators $\Aop:L^2(\Omega_1) \rightarrow L^2(\Omega_2)'$ that map between function spaces on different domains $\Omega_1$ and $\Omega_2$, and even operators that map between domains with different spatial dimensions. In contrast, \eqref{eq:translate2} does not naturally generalize to operators that map between function spaces on different domains, because the formula $y-x+x'$ requires $y \in \Omega_2$ and $-x+x' \in \Omega_1$ to be added together.
